\LARGE \bf Efficient Sampling for Grasp Quality Evaluation on Gaussian Process Implicit Surface Representations [v-12 09-30-2014]

### 2014-10-01 paper.tex
some edits

\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
Consider a robot packing boxes in a shipping warehouse environment. The robot will frequently encounter objects that it has not seen before. The robot will have to plan stable grasps without any prior information other than its sensor data. As seen in Fig. \ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations. Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail. To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity%%PA: --> spelling
 in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %%ZM: fixed

@@

More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the awards seen. At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$. This happens until a stopping signal is given at which point an arm (or grasp plan) is chosen based on a recommendation strategy $\zeta_t \in \lbrace 1,...,K \rbrace$.

>>>>

\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
Consider a robot packing boxes in a shipping warehouse environment. The robot will frequently encounter objects that it has not seen before. The robot will have to plan stable grasps without any prior information other than its sensor data. As seen in Fig. \ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations. Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail. To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty%%PA: --> spelling %%ZM: fixed
 in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %%ZM: fixed

@@

More formally an agent is given a set prior distributions $\mathcal{P}(1,...,K)$ for the K arms based on the rewards seen. At each interval an arm $I_t$ is pulled based on some allocation strategy $\psi_t \in \lbrace 1,...,K \rbrace$. This happens until a stopping signal is given at which point an arm (or grasp plan) is chosen based on a recommendation strategy $\zeta_t \in \lbrace 1,...,K \rbrace$.
